### 2019-04-29 manuscript.tex

— Suggestions —
- empowering community, engaging community leaders and other strategies \citeBergDeni13b}
- MC vs. FGC.  Considering the acceptance of Alternative rights of passage \cite{GaluKama15} without criminalize the practice. (I'm not sure if I'm comfortable with this position, but it is an alternative.) vs. focused on empowerment, and campaigns to recruit change agents from within communities (to eradicate FGC) \cite{ShelHern13, Will18}
- modelling by plotting empirical data to study threshold/tipping point.
- redesign questions of fgc benefits in DHS
- inviting faced women migrated to western society to participate in fgc intervention campaign.  For example,  attitude change: "migrating to and living in Sweden facilitates a transition in attitudes regarding FGC" \cite{WahlJohn17}, and initiating “participatory campaign and education”  (an idea from \ciet{MackLeJe08}’s “participatory human rights education” and Boston’s), including women’s empowerment and horizontal involvement (vs. trickle-down strategy)
- \cite{MackLeJe08}”coordinated community abandonments (Dagne 2008, http://www.kmgselfhelp.org/hotissues.html). Both human rights deliberation and coordinated community abandonment are necessary for change. National programmes in Egypt and Sudan are promoting positive human rights messages and discussions at national, regional, and local levels, and are experimenting with a variety of coordinated abandonment through community dialogue efforts at the local level. “ (use \cite{Dagn09, MackLeJe08} for this idea)

@@

\bibliography{manual}

@@

Suggestions: pricking (type IV\cite{WHO08})\cite{WahlJohn17a, WahlJohn17b} and medical FGC \cite{KimaShell18} vs. no-tolerance, fgc vs. mc \cite{WahlEsse18}?  We suggest to position ourselves in a context where male circumcision (MC) is practices and accepted; to consider the differences of a prick of FGC and MC; to comprehend the outcomes of abolishing FGC vs. changing FGC practices.
\cite{WahlEsse18}:  from sameness to differences, a global multicultural approach especially during the international migration across the globe.

>>>>

— Suggestions —
- empowering community, engaging community leaders and other strategies \cite{BergDeni13b}
- MC vs. FGC.  Considering the acceptance of Alternative rights of passage \cite{GaluKama15} without criminalize the practice. (I'm not sure if I'm comfortable with this position, but it is an alternative.) vs. focused on empowerment, and campaigns to recruit change agents from within communities (to eradicate FGC) \cite{ShelHern13, Will18}
- modelling by plotting empirical data to study threshold/tipping point.
- redesign questions of fgc benefits in DHS
- inviting faced women migrated to western society to participate in fgc intervention campaign.  For example,  attitude change: "migrating to and living in Sweden facilitates a transition in attitudes regarding FGC" \cite{WahlJohn17}, and initiating “participatory campaign and education”  (an idea from \ciet{MackLeJe08}’s “participatory human rights education” and Boston’s), including women’s empowerment and horizontal involvement (vs. trickle-down strategy)
- \cite{MackLeJe08}”coordinated community abandonments (Dagne 2008, http://www.kmgselfhelp.org/hotissues.html). Both human rights deliberation and coordinated community abandonment are necessary for change. National programmes in Egypt and Sudan are promoting positive human rights messages and discussions at national, regional, and local levels, and are experimenting with a variety of coordinated abandonment through community dialogue efforts at the local level. “ (use \cite{Dagn09, MackLeJe08} for this idea)

@@

\bibliography{refs}

@@

Suggestions: pricking (type IV\cite{WHO08})\cite{WahlJohn17a, WahlJohn17b} and medical FGC \cite{KimaShel18} vs. no-tolerance, fgc vs. mc \cite{WahlEsse18}?  We suggest to position ourselves in a context where male circumcision (MC) is practices and accepted; to consider the differences of a prick of FGC and MC; to comprehend the outcomes of abolishing FGC vs. changing FGC practices.
\cite{WahlEsse18}:  from sameness to differences, a global multicultural approach especially during the international migration across the globe.
